Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-19 bbbq_article.tex
COVID-19 TMHs is back in again, using pureseqtmr
Show number of TMHs, cite 'pureseqtmr'

%\begin{figure}[!htbp]
%  \includegraphics[width=\textwidth]{tmhs/tmhs.png}
%  \caption{
%    Location of amino acids of reference COVID-19 proteome.
%    Note that ORF1a results in multiple proteins, 
%    as shown in figure \ref{fig:covid_genome_and_proteome}.
%    Legend: i = inside (cytosolic side), m = membrane, o = outside (extracellular side)
%    \richel{This is real data}
%  }
%  \label{fig:covid_locatome}
%\end{figure}

>>>>

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{tmhs/tmhs.png}
  \caption{
    Location of amino acids of reference COVID-19 proteome.
    Note that ORF1a results in multiple proteins, 
    as shown in figure \ref{fig:covid_genome_and_proteome}.
    Legend: i = inside (cytosolic side), m = membrane, o = outside (extracellular side)
    \richel{This is real data}
  }
  \label{fig:covid_topology}
\end{figure}

\begin{table}[!htbp]
  \input{tmhs/covid_tmhs.latex}
  \caption{
    Number of TMHs per COVID-19 ORF,
    using 'pureseqtmr' \cite{pureseqtmr}
  }
  \label{table:covid_tmhs}
\end{table}
